\documentclass[]{article}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{hyperref}
\usepackage[all]{xy}
\usepackage{color}
\usepackage{fullpage}

\newcommand{\taylor}[1]{{\color{blue} \sf $\spadesuit\spadesuit\spadesuit$ Taylor: [#1]}}
%\newcommand{\collab}[1]{{\color{red} \sf $\spadesuit\spadesuit\spadesuit$ collab1: [#1]}}  %Dear Collaborator, make a macro for yourself here. 
\newcommand{\todo}[1]{{\color{purple} \sf $\spadesuit\spadesuit\spadesuit$ TODO: [#1]}}

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[subsection]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{question}[theorem]{Question}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{remarks}[theorem]{Remarks}
\newtheorem{warning}[theorem]{Warning}


%opening


\begin{document}
	
	\begin{center}
		{\Large \sc Dupuy -- Math 1077  -- List of Stories  }\\
		last updated: \today
	\end{center}

Here is a list of stories I want to tell. 
\begin{enumerate}
	\item COUNTING 
	\begin{enumerate}
		\item More people will have the same birthday than you would expect.
		\item $1+10^{-16}=1$ on Calculators.
		\item The number of sandwiches you can create is on the scale of the number of particles in the universe.
		\item How many ways are there to rewrite the word ``BANANA''?
		\item Galton Board Demonstration/Plinko on \emph{The Price Is Right}.
	\end{enumerate}
	
	
	\item PROBABILITY 
	\begin{enumerate}
		\item \emph{Cash WinFall} aka \emph{Jerry and Marge Go Large} aka The MIT Lottery Kids.
		\item You don't know how to fake a cointoss; $p$-value hacking, its bad and its everywhere.
		\item \emph{Let's Make a Deal} and The Monty Hall Problem. (Your intuition about probability is broken.)
		\item Utility Functions: why if you never miss a plane you are probably doing it wrong.
		\item Things I want to do but haven't in the past: 	Biased Sampling: Berkson's Fallacy, Survivor Bias and the Baltimore Stock Broker; Statistical-Logic and Logic-Logic are not the same; Cointossing is a microcosm for everything;  How the Allies calculated the number of German tanks in World War 2. 
	\end{enumerate}
\item VOTING
\begin{enumerate}
	\item Voting theory, ranked choice voting.
	\item Ross Perot, Ralph Nader, and RFK Jr. (the guy who dumped a dead bear in Central Park).
	\item Slime Molds use ranked choice voting to make decisions.
	\item Burlington's 2009 Mayoral Election.
	\item No perfect voting system exists.
\end{enumerate}

	\item GRAPHS AND NETWORKS
	\begin{enumerate}
		\item The Seven Bridges of Koenigsburg Puzzle [and the House Walking Puzzle].
		\item The Traveling Salesman Problem (and what keeps your credit card information safe).
		\item The Three Houses and Three Utilities Puzzle.
		\item How many colors do you need to make a world map?
	\end{enumerate}
	
	\item SYMMETRY
	\begin{enumerate}
		\item The Prisoner Puzzle: \url{https://www.youtube.com/watch?v=hYSaEyPK5MQ}
		\item The Hummer Shuffle: \url{https://web.northeastern.edu/seigen/11Magic/Hummer/Hummer.html}
		\item The Golden Ratio
	\end{enumerate}
\end{enumerate}


\end{document}
